---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regport

<!-- badges: start -->
<!-- badges: end -->

The goal of regport is to provides R6 classes, methods and utilities to construct,
    analyze, summarize, and visualize regression models (CoxPH and GLMs).

## Installation

You can install the development version of regport like so:

```r
remotes::install_github("ShixiangWang/regport")
```

## Simple case

This is a basic example which shows you how to build and visualize a Cox model.

Prepare data:

```{r}
library(regport)
library(survival)

lung = survival::lung
lung$sex = factor(lung$sex)
```
Create a model:

```{r}
model = REGModel$new(
  lung,
  recipe = list(
    x = c("age", "sex"),
    y = c("time", "status")
  )
)

model
```

You can also create it with formula:

```{r}
model = REGModel$new(
  lung,
  recipe = Surv(time, status) ~ age + sex
)

model
```

Visualize it:

```{r, fig.width=4, fig.width=6}
model$plot()
```

Visualize with more nice forest plot.

```{r dpi=300}
model$get_forest_data()
model$plot_forest()
```

