---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regport

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/regport)](https://cran.r-project.org/package=regport) 
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R-CMD-check](https://github.com/ShixiangWang/regport/workflows/R-CMD-check/badge.svg)](https://github.com/ShixiangWang/regport/actions) 
[![](https://cranlogs.r-pkg.org/badges/grand-total/regport?color=orange)](https://cran.r-project.org/package=regport) 
[![Closed issues](https://img.shields.io/github/issues-closed/ShixiangWang/regport.svg)](https://github.com/ShixiangWang/regport/issues?q=is%3Aissue+is%3Aclosed) 
[![Hits](https://hits.seeyoufarm.com/api/count/incr/badge.svg?url=https%3A%2F%2Fgithub.com%2FShixiangWang%2Fregport&count_bg=%2379C83D&title_bg=%23555555&icon=&icon_color=%23E7E7E7&title=hits&edge_flat=false)](https://hits.seeyoufarm.com)

<!-- badges: end -->

The goal of regport is to provides R6 classes, methods and utilities to construct,
analyze, summarize, and visualize regression models (CoxPH and GLMs).

## Installation

You can install the development version of regport like so:

```r
remotes::install_github("ShixiangWang/regport")
```

## Simple case

This is a basic example which shows you how to build and visualize a Cox model.

Prepare data:

```{r}
library(regport)
library(survival)

lung = survival::lung
lung$sex = factor(lung$sex)
```
Create a model:

```{r}
model = REGModel$new(
  lung,
  recipe = list(
    x = c("age", "sex"),
    y = c("time", "status")
  )
)

model
```

You can also create it with formula:

```{r}
model = REGModel$new(
  lung,
  recipe = Surv(time, status) ~ age + sex
)

model
```

Visualize it:

```{r, fig.width=4, fig.width=6}
model$plot()
```

Visualize with more nice forest plot.

```{r dpi=300}
model$get_forest_data()
model$plot_forest()
```

## Batch processing models

```{r dpi=300}
ml <- REGModelList$new(
  data = mtcars,
  y = "mpg",
  x = c("factor(cyl)", colnames(mtcars)[3:5]),
  covars = c(colnames(mtcars)[8:9], "factor(gear)")
)
ml
ml$build(f = "gaussian")
str(ml$result)
str(ml$forest_data)

ml$plot_forest(ref_line = 0, xlim = c(-15, 8))
```

## Coverage

```{r}
covr::package_coverage()
```

## LICENSE

(MIT) Copyright (c) 2022 Shixiang Wang

